Analysis after review

### 2020-04-28 reports/DRM_exp/analysis_DRM_after_review.Rmd
some new figures regarding context entropy

>>>>

## Context entropy

```{r}
cont_entropy <- read_csv(here("data/exp_DRM1/cats_entrophy.csv"), col_names = F) %>% rename(category = X1, cont_entropy = X2) %>% mutate(category = str_replace(category, "_", " "))
df_cont_entropy <- df %>% left_join(cont_entropy, by = "category") 
df_cont_entropy %>% 
  ggplot(aes(x = category, y = correct, col = type, group = type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = "mean", geom = "line")

df_cont_entropy %>% 
  filter(type != "target") %>% 
  group_by(category,type) %>% 
  summarize(FA = mean(1-correct), cont_entropy = mean(cont_entropy)) %>% 
  group_by(category) %>% 
  summarize(diff_FA = FA[type == "close distractor"]-FA[type == "far distractor"],
            cont_entropy = mean(cont_entropy)) %>% 
  ggplot(aes(x = diff_FA, y = cont_entropy, label = category)) +
  geom_point()+
  ggrepel::geom_label_repel()

df_cont_entropy %>% 
  filter(type == "close distractor") %>% 
  group_by(category) %>% 
  summarize(FA = mean(1-correct), cont_entropy = mean(cont_entropy)) %>% 
  ggplot(aes(x = FA, y = cont_entropy, label = category)) +
  geom_point()+
  ggrepel::geom_label_repel()  + 
  ggtitle("Close distractors")

df_cont_entropy %>% 
  filter(type == "far distractor") %>% 
  group_by(category) %>% 
  summarize(FA = mean(1-correct), cont_entropy = mean(cont_entropy)) %>% 
  ggplot(aes(x = FA, y = cont_entropy, label = category)) +
  geom_point()+
  ggrepel::geom_label_repel() + 
  ggtitle("Far distractors")
